Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-14 ieee_paper.tex
Added conclusion.

\section{Conclusions and Perspectives}
\label{sec:ccl}

The conclusion goes here. this is more of the conclusion

future works: gpu. more applications. more nnz/row.

\section*{Acknowledgment}

The authors would like to thank...
more thanks here

>>>>

\section{Conclusion}
\label{sec:ccl}
In the previous sections, we have explored in the practical implementation on a MIC architecture of multiple derivative operators acting on multiple vectors within the context of RBF-RD. Each derivative has an associated sparse matrix with a fixed number
of non-zeros on each row. While computing a single derivative of multiple functions is rather common (vectorization occurs over the vectors), we accelerate the algorithm further by considering multiple derivatives with corresponding
matrices with identical adjacency graphs. We specialize to four matrices and four derivatives, with 16 outputs, 
computed as a sum of outer products.

Using a matrix with $64^3$ (or $96^3$ rows, we achieve a speedup of xxx relative to the base case of one derivative and one function (1/1/ case), releative to a potential speedup of 16. We have achieved a speed 100 Gflops on 60 nodes using 240 threads, or a speed of 61\% of maximum possible performance. The maximum possible speed for the 1/1 case is around 40 Gflops, of which we achieve 20 Gflops. On matrices that exceed cache, a reverse Cuthill-McKee is applied
to reduce the bandwidth, with an associated speedup of 30\% up to 135 Gflops. Our optimal implementation makes 
use of the AVX instruction set, which makes use of swizzling and channel swapping operations for an extremely 
efficient tensor product implementation. A straightforward implementation without AVX run at around 35 Gflops, 
or 16\% of peak performance. RCM has no effect because the number of floating point operations is excessive (the 
algorithm does not fill the vector registers to capacity).

In a future work, we will examine the effect of larger stencil sizes, double precision, and the actual cost
of computing the derivatives within a fluid simulation using RBF-FD.

\section*{Acknowledgment}
The first and last authors acknowledge NSF funding under NSF grant DMS-\#0934331 (FSU).
